
%\clearpagebefore
%\phantomsection
%\addcontentsline{toc}{chapter}{Bibliography}
%\begin{onehalfspacing}
%\bibliographystyle{ieeetr}
%\bibliography{ref}
%\bibliography{reference}
%\end{onehalfspacing}

%\begin{thebibliography}{00}
%\end{thebibliography}

\begin{thebibliography}{00}
\addcontentsline{toc}{chapter}{\bibname}

% 영문저널의 경우
%    \bibitem{ref1} B. Jeon and J. Jeong, ``Blocking artifacts
%    reduction in image compression with block boundary discontiunity
%    criterion,'' {\em IEEE Transactions on Circuits and Systems for
%    Video Tech.}, vol. 8, no.3, pp. 345-357, June 1998.

% 영문학술대회의 경우
%    \bibitem{ref2} W. G. Jeon and Y. S. Cho, ``An equalization
%    technique for OFDM and MC-CDMA in a multipath fading channels,''
%    in {\em Proceedings of IEEE Conference on Acoustics, Speech and
%    Signal Processing}, Munich, Germany, May 1997. pp. 2529-2532.

% 단행본의 경우
%    \bibitem{ref4} C. Mead and L. Conway, {\em Introduction to VLSI
%    Systems}, Addison-Wesley, Boston, 1994.

% URL
%    \bibitem{ref5} The SolarMESH Network,
%    http://owl.mcmater.ca/solarmesh

% Technical Report의 경우
%    \bibitem{ref6} K. E. Elliott and C. M. Greene, ``A local adaptive
%    protocol,'' Argonne National Laboratory, Argonne, France,
%    Technical Report 916-1010-BB, 1997.

% 학위논문의 경우
%    \bibitem{ref7} T. Kim, ``Scheduling and Allocation Problems in
%    High-level Synthesis,'' Ph. D. Dissertation, ECE Department,
%    Univ. of Illinois at U-C, 1993.

% 특허의 경우
%    \bibitem{ref8} Sunghyun Choi, ``Wireless MAC protocol based on a
%    hybrid combination of slot allocation, token passing, and
%    polling for isochronous traffic,'' U.S. Patent No. 6,795,418,
%    September 21, 2004.

% 표준
%    \bibitem{ref9} IEEE Std. 802.11-1999, Part 11: Wireless LAN
%    Medium Access Control (MAC) and Physical Layer (PHY)
%    specifications, Reference number ISO/IEC 8802-11:1999(E), IEEE
%    Std. 802.11, 1999 edition, 1999.

\bibitem{FTL}
T. Chung, D. Park, S. Park, D. Lee, S. Lee and H. Song,
``A Survey of Flash Translation Layer,''
\emph{Journal of Systems Architecture,} vol. 55, no. 5, pp. 332-343, 2009.

\bibitem{MooresLaw}
A. Chien and V. Karamcheti,
``Moore's Law: The First Ending and a New Beginning,''
\emph{IEEE Computer Magazine,} vol. 46, no. 12, pp. 48-53, 2013.

\bibitem{HotCold}
J. Hsieh, T. Kuo, and L. Chang,
``Efficient Identification of Hot Data for Flash Memory Storage Systems,''
\textit{ACM Transactions on Storage}, vol. 2, no. 1, pp. 22-40, 2006.

\bibitem{DPES}
J. Jeong, S. Hahn, S. Lee, and J. Kim,
``Lifetime Improvement of NAND Flash-based Storage Systems Using Dynamic Program and Erase Scaling,''
In \emph{Proceedings of the 16th USENIX Conference on File and Storage Technologies (FAST)}, 2014.

\bibitem{InlineDedup}
Deepstorage.net,
``Storage Efficiency Imperative: An In-Depth Review of Storage Efficiency Technologies
and the Solidfire Approach,''
\url{http://www.deepstorage.net/NEW/reports/SolidFireStorageEfficiency.pdf}, 2012.

\bibitem{multibloom}
D. Park, and D. Du,
``Hot Data Identification for Flash-Based Storage Systems Using Multiple Bloom Filters,''
In \textit{Proceedings of the IEEE Symposium on Mass Storage Systems and Technologies (MSST)}, 2011.

\bibitem{updatefreq}
R. Stoica, J. Levandoski, and P. Larson,
``Identifying Hot and Cold Data in Main-Memory Databases,''
In \textit{Proceedings of the IEEE International Conference on Data Engineering (ICDE)}, 2013.

\bibitem{writehot}
Y. Luo, Y. Cai, S. Ghose, J. Choi, and O. Mutlu,
``Warm: Improving Nand Flash Memory Lifetime with Write-Hotness Aware Retention Management,''
In \textit{Proceedings of the IEEE Symposium on Mass Storage Systems and Technologies (MSST)}, 2015.

\bibitem{cacheenergy}
N. Bellas, I. Hajj, and C. Polychronopoulos,
``Using Dynamic Cache Management Techniques to Reduce Energy in a High-Performance Processor,''
In \textit{Proceedings of the ACM International Symposium on Low Power Electronics and Design (ISLPED)}, 1999.

\bibitem{cachemngmt}
A. Lai, and B.Falsafi,
``Selective, Accurate, and Timely Selfinvalidation Using Last-Touch Prediction,''
In \textit{Proceedings of the International Symposium on Computer Architecture (ISCA)}, 2000.

\bibitem{memoryprefetching}
T. Sherwood, S. Sair, and B. Calder,
``Predictor-Directed Stream Buffers,''
In \textit{Proceedings of the International Symposium on Computer Architecture (ISCA)}, 2000.

\bibitem{DAC}
M. Chiang, P. Lee, R. and Chang,
``Using Data Clustering to Improve Cleaning Performance for Flash Memory,''
\textit{Software-Practice \& Experience}, vol. 29, no. 3, pp. 267-290, 1999.

\bibitem{WriteAmplification}
X. Hu, E. Eleftheriou, R. Haas, I. Iliadis, and R. Pletka,
``Write Amplification Analysis in Flash-Based Solid State Drives,''
In \textit{Proceedings of the ACM International Systems and Storage Conference (SYSTOR)}, 2009

\bibitem{GCGreedy}
W. Bux, and I. Iliadis,
``Performance of Greedy Garbage Collection in Flash-Based Solid-State Drives,''
\textit{Performance Evaluation}, vol. 67, no. 11, pp. 1172-1186, 2010.

\bibitem{GCVictim}
C. Tsao, Y. Chang, and M. Yang,
``Performance Enhancement of Garbage Collection for Flash Storage Devices: 
An Efficient Victim Block Selection Design'',
In \textit{Proceedings of the Annual Design Automation Conference (DAC)}, 2013.

\bibitem{GCTTFlash}
S. Yan, H. Li, M. Hao, M. Tong, S. Sundararaman, A. Chien, and H. Gunawi,
``Tiny-tail Flash: Near-perfect Elimination of Garbage Collection Tail Latencies in NAND SSDs'',
In \textit{Proceedings of the USENIX Conference on File and Storage Technologies (FAST)}, 2017.


\bibitem{JiTGC}
S. Hahn, S. Lee, and J. Kim,
``To Collect or Not to Collect: Just-in-Time Garbage Collection for High-Performance SSDs with Long Lifetimes'',
In \textit{Proceedings of the Design Automation Conference (DAC)}, 2015.

\bibitem{ShadowGC}
J. Cui, Y. Zhang, J. Huang, W. Wu, and J. Yang,
``ShadowGC: Cooperative Garbage Collection with Multi-Level Buffer for Performance Improvement 
in NAND flash-based SSDs'',
In \textit{Proceedings of the Design, Automation and Test in Europe Conference and Exhibition (DATE)}, 2018.

\bibitem{T10}
``SCSI Block Commnads-4 (SBC-4)'',
\url{http://www.t10.org/cgi-bin/ac.pl?t=f&f=sbc4r15.pdf}.

\bibitem{MultiStream}
J. Kang, J. Hyun, H. Maeng, and S. Cho,
``The Multi-streamed Solid-State Drive'',
In \textit{Proceedings of the Workshop on Hot Topics in Storage and File Systems (HotStorage)}, 2014.

\bibitem{Level}
F. Yang, D. Dou, S. Chen, M. Hou, J. Kang, and S. Cho,
``Optimizing NoSQL DB on Flash: A Case Study of RocksDB'',
In \textit{Proceedings of IEEE the International Conference on Scalable Computing
and Communications (ScalCom)}, 2015.

\bibitem{vStream}
H. Yong, K. Jeong, J. Lee, J. Kim,
``vStream: Virtual Stream Management for Multi-streamed SSDs'',
In \textit{Proceedings of the USENIX Workshop on Hot Topics in Storage
and File Systems (HotStorage)}, 2018.

\bibitem{FStream}
E. Rho, K. Joshi, S. Shin, N. Shetty, J. Hwang, S. Cho. and D. Lee,
``FStream: Managing Flash Streams in the File System'',
In \textit{Proceedings of the USENIX Conference on File and Storage Technologies (FAST)}, 2018.

\bibitem{AutoStream}
J. Yang, R. Pandurangan, C. Chio, and V. Balakrishnan,
``AutoStream: Automatic Stream Management for Multi-streamed SSDs'',
In \textit{Proceedings of the ACM International Systems and Storage Conference (SYSTOR)}, 2017.

\bibitem{RocksDB}
Facebook,
\url{https://github.com/facebook/rocksdb}.

\bibitem{Cassandra}
Apache Cassandra,
\url{http://cassandra.apache.org}.


\bibitem{PC}
C. Gniady, A. Butt, and Y. Hu,
``Program-Counter-based Pattern Classification in Buffer Caching'',
In \textit{Proceedings of the Symposium on Operating Systems Design and Implementation (OSDI)}, 2004.

\bibitem{PC2}
F. Zhou, J. Behren, and E. Brewer,
``Amp: Program Context Specific Buffer Caching,''
In \textit{Proceedings of USENIX Annual Technical Conference (ATC)}, 2005.

\bibitem{PCHa}
K. Ha, and J. Kim,
``A Program Context-Aware Data Separation Technique for Reducing Garbage Collection Overhead in NAND Flash Memory,''
In \textit{Proceedings of International Workshop on Storage Network Architecture 
and Parallel I/Os (SNAPI)}, 2011.

\bibitem{kmeans}
J. Hartigan, and M. Wong,
``Algorithm as 136: A k-means Clustering Algorithm'',
\textit{Journal of the Royal Statistical Society. Series C (Applied Statistics)},
vol. 28, no. 1, pp. 100-108, 1979.

\bibitem{LSM}
P. ONeil, E. Cheng, D. Gawlick, and E. ONeil,
``The Log-Structured Merge-Tree (LSM-Tree)'',
\textit{Acta Informatica}, vol. 33, no. 4, pp. 351-385, 1996.

\bibitem{TRIM}
J. Corbet,
Block Layer Discard Requests,
\url{https://lwn.net/Articles/293658/}.

\bibitem{NVMe}
NVM Express Revision 1.3,
\url{http://nvmexpress.org/wp-content/uploads/NVM_Express_Revision_1.3.pdf}.

\bibitem{TCM}
S. Frank,
``Tightly Coupled Multiprocessor System Speeds Memory-Access Times'',
\textit{Electronics}, vol. 57, no. 1, 1984.

\bibitem{SQLite}
SQLite,
\url{https://www.sqlite.org/index.html}.


\bibitem{GCC}
R. Stallman, and GCC Developer Community,
Using the GNU Compiler Collection for GCC version 7.3.0,
\url{https://gcc.gnu.org/onlinedocs/gcc-7.3.0/gcc.pdf}.

\bibitem{AMF}
S. Lee, M. Liu, S. Jun, S. Xu, J. Kim, and Arvind.
``Application-Managed Flash''.
In \textit{Proceedings of the USENIX Conference on File and Storage
Technologies (FAST)}, 2016.


\bibitem{PM963}
Samsung, Samsung SSD PM963, 
\url{https://www.compuram.de/documents/datasheet/Samsung_PM963-1.pdf}

\bibitem{JNI}
S. Liang,
Java Native Interface: Programmer's Guide and Specification,
1999.

\bibitem{MySQL}
MySQL,
\url{https://www.mysql.com}.

\bibitem{PostgreSQL}
PostgreSQL,
\url{https://www.postgresql.org}.

\bibitem{OpenJDK}
OpenJDK,
\url{http://openjdk.java.net/}.

\bibitem{nvmecli}
NVM-Express User Space Tooling For Linux,
\url{https://github.com/linux-nvme/nvme-cli}.

\bibitem{YCSB}
B. Cooper, A. Silberstein, E. Tam, R. Ramakrishnan, and R. Sears,
``Benchmarking Cloud Serving Systems with YCSB'',
In \textit{Proceedings of the ACM Symposium on Cloud Computing (SoCC)}, 2010.

\bibitem{TPCC}
The Transaction Processing Performance Council,
Benchmark C,
\url{http://www.tpc.org/tpcc/default.asp}. 

\bibitem{PCStream} 
T. Kim, S. Hahn, S. Lee, J. Hwang, J. Lee and J. Kim,
``PCStream: Automatic Stream Allocation Using Program Contexts'',
In \textit{Proceedings of the USENIX Workshop on Hot Topics in Storage
and File Systems (HotStorage)}, 2018.

\bibitem{MonetDB}
MonetDB,
\url{https://www.monetdb.org}.

\bibitem{mmap}
Linux Programmer's Manual,
mmap(2) - map files or devices into memory,
\url{http://man7.org/linux/man-pages/man2/mmap.2.html}.


\bibitem{tlc}
M. Goldman et al.,
``25nm 64Gb 130mm2 3bpc NAND Flash Memory,''
in \textit{Proceedings of 3rd International Memory Workshop}, 2011.

%\bibitem{8kpage}
%H. Kim et al.,
%``A 159mm 32nm 32Gb MLC NAND-Flash Memory with 200MB/s Asynchronous DDR Interface,''
%in \textit{Proceedings of International Solid-State Circuits Conference}, 2010.

\bibitem{16kpage}
Y. Li et al.,
``128Gb 3b/Cell NAND Flash Memory in 19nm Technology with 18MB/s Write Rate and 400Mb/s Toggle Mode,''
in \textit{International Solid-State Circuits Conference}, 2012.

%\bibitem{BAST} 
%J. Kim et al.,
%``A Space-Efficient Flash Translation Layer for Compact Flash Systems,''
%in \textit{IEEE Transactions on Consumer Electronics}, vol. 48, no. 2, pp. 366-375, 2002.

\bibitem{FAST} 
S.-W. Lee et al.,
``A Log Buffer Based Flash Translation Layer Using Fully Associative Sector Translation,''
in \textit{ACM Transactions on Embedded Computing Systems}, vol. 6, no. 3, 2007.

%\bibitem{LAST}
%S. Lee, D. Shin, Y.-J. Kim, and J. Kim,
%``LAST: Locality-Aware Sector Translation for NAND Flash Memory-Based Storage Systems,''
%\textit{ACM SIGOPS Operating Systems Review}, 2008.

\bibitem{md6}
R.L. Rivest et al.,
``The MD6 hash function - a proposal to NIST for SHA-3,''
\url{http://groups.csail.mit.edu/cis/md6/}, Submission to NIST, 2008.

\bibitem{sm825}
K. OBrien,
``Samsung SSD SM825 Enterprise SSD Review,''
\url{http://www.storagereview.com/samsung_ssd_sm825_enterprise_ssd_review}, 2012.

\bibitem{caftl}
F. Chen, T. Luo, and X. Zhang, 
``CAFTL: A Content-Aware Flash Translation Layer Enhancing the Lifespan of Flash Memory Based Solid State Drives,''
in \textit{Proceedings of USENIX Conference on File and Storage Technologies (FAST)}, 2011.

\bibitem{value-locality}
A. Gupta, R. Pisolkar, B. Urgaonkar, and A. Sivasubramaniam,
``Leveraging Value Locality in Optimizing NAND Flash-Based SSDs,''
in \textit{Proceedings of USENIX Conference on File and Storage Technologies (FAST)}, 2011.

\bibitem{order-merge}
Z. Chen and K. Shen, 
``OrderMergeDedup: Efficient, Failure-Consistent Deduplication on Flash,'' 
in \textit{Proceedings of USENIX Conference on File and Storage Technologies (FAST)}, 2016.

\bibitem{cachededup}
W. Li, G. Jean-Baptise, J. Riveros, and G. Narasimhan, 
``CacheDedup: In-line Deduplication for Flash Caching,''
in \textit{Proceedings of USENIX Conference on File and Storage Technologies (FAST)}, 2016.

\bibitem{dedupv1}
D. Meister and A. Brinkmann,
``dedupv1: Improving Deduplication Throughput using Solid State Drives,''
in \textit{Proceedings of IEEE Symposium on Mass Storage Systems and Technologies (MSST)}, 2010.

\bibitem{dong}
W. Dong et al.,
``Tradeoffs in Scalable Data Routing for Deduplication Clusters,''
in \textit{Proceedings of USENIX Conference on File and Storage Technologies (FAST)}, 2011

%\bibitem{idedup}
%K. Srinivasan and T. Bisson, G. Goodson, K. Voruganti,
%``iDedup: Latency-aware, Inline Data Deduplication for Primary Storage,''
%in \textit{Proceedings of 10th USENIX Conference on File and Storage Technologies}, 2012.

\bibitem{dftl}
A. Gupta, Y. Kim and B. Urgaaonkar, 
``DFTL: A Flash Translation Layer Employing Demand-based Selective Caching of Page-level Address Mappings,''
in \textit{Proceedings of International Conference on Architectural Support for Programming Languages and
Operating Systems}, 2009.

\bibitem{diskbottleneck}
B. Zhu, K. Li, and H. Patterson,
``Avoiding the disk bottleneck in the Data Domain deduplication file system,''
in \textit{Proceedings of USENIX Conference on File and Storage Technologies (FAST)}, 2008.



\end{thebibliography}
